### 2025-11-09 sections/4-results.tex
brought back Partition

For each of the ANN-benchmark datasets and Random, Fig.~\ref{fig:results:indexing} reports the time taken for each algorithm to build its index and to tune any hyper-parameters to maximize recall.

\begin{figure}[h]
  \centering
  \vskip -0.2in
  \subfloat[Fashion-MNIST]{
    \includegraphics[width=0.24\textwidth]{images/indexing/fashion-mnist-indexing.png}
    \label{fig:results:fashion-mnist-indexing}
  }
  \subfloat[Glove-25]{=
    \includegraphics[width=0.24\textwidth]{images/indexing/glove-25-indexing.png}
    \label{fig:results:glove-25-indexing}
  }

>>>>

For each of the vector datasets, Fig.~\ref{fig:results:indexing} reports the time taken for each algorithm to build its index assuming that the hyper-parameters are set to maximize recall.

\begin{figure}[h]
  \centering
  \vskip -0.2in
  \subfloat[Fashion-MNIST]{
    \includegraphics[width=0.24\textwidth]{images/indexing/fashion-mnist-indexing.png}
    \label{fig:results:fashion-mnist-indexing}
  }
  \subfloat[Glove-25]{
    \includegraphics[width=0.24\textwidth]{images/indexing/glove-25-indexing.png}
    \label{fig:results:glove-25-indexing}
  }
